\documentclass{article}

\usepackage{subfiles}

\title{A Level CS}
\author{Michael Hallam}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\newpage

	\section{About the book}
	Once upon a time, I was an A Level CS student. In my time studying, I (like many others in my class) bemoaned the lack of any good, comprehensive, cheap textbooks. Unlike in Maths or Physics, where the content was known and resources were widely available, CS just didn't have quite the same thing.

	I have devised this textbook to fill this gap. I plan to release both the pdf source version and the \LaTeX{} source for free. I give permission to adapt and use this resource for free, but I do \textbf{not} give permission for it to be sold for profit.

	There won't be any example questions in the book - past papers and teacher only resources exist that can fill this gap nicely. I would recommend doing questions with each section - practice makes perfect \textit{etc etc}. The book will be based on the \textbf{AQA} spec.
	
	If you have any improvements or requests for new features, please email me at michael \textit{dot} hallam3 \textit{at} gmail \textit{dot} com. Please also email me if there's part of another spec you feel isn't covered in this book that you would like covered. Please also feel free to let me know if you use this textbook - I would love to hear about it doing some good in the world!

	\newpage

	\tableofcontents

	\pagenumbering{arabic}

	\section{Fundamentals of Functional Programming}
	\subfile{sections/fp.tex}

\end{document}

